---
title: "Assignment_02_Example"
author: "Tushar Dhanorkar"
format: html
editor: visual
---

## **Step 1: Create a new RStudio Project**

-   Create a new RStudio Project. In this folder, create a simple qmd file called `example.qmd` that can be knitted into a HTML file. Show the result of the knitted file.

-   I then created a simple *example.qmd* file with:

    -   A YAML header specifying title, author and html format

    -   Two R code chunks demonstrating basic calculations

-   The file was rendered into HTML using the Render button which executes all code chunks and produces a formatted HTML document.

-   Save this file as example.qmd

Addition Operation

```{r}
1 + 1
```

Multiplication Operation

```{r}
#| echo: false
2 * 2
```

<<<<<<< HEAD
## New Section on main

This section was added on main and will conflict with testbranch.

```{r}
y <- c(10, 20, 30, 40, 50)
sum(y)
=======
#### Adding new section:

working on testbranch

```{r}
x <- c(10, 20, 30, 40, 50)
mean(x)
>>>>>>> testbranch
```
